### 2017-05-25 manuscript/usses_water_ms.Rmd
updates authors

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Andrew R. Kleinhesselink\textsuperscript{2}, Bret Taylor\textsuperscript{3}, and Peter B. Adler\textsuperscript{1}}

@@

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah 84322}} \\
\textit{\small{\textsuperscript{2}Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles, California xxxxx}} \\
\textit{\small{\textsuperscript{3}U.S. Sheep Experiment Station, Range Sheep Production Efficiency Research Unit, USDA-ARS, Dubois, Idaho 83423}}

>>>>

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Andrew R. Kleinhesselink\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah 84322}} \\
\textit{\small{\textsuperscript{2}Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles, California xxxxx}}
